---
title: "Art Collections"
author: "Eric Leung"
date: "2021-01-13"
output: html_document
---

## Setup

```{r setup, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Utilities
library(tidytuesdayR)
library(readr)
library(here)

# Data wrangling
library(dplyr)
library(tidyr)
library(tidytext)

# plotting libraries
library(ggplot2)
library(visdat)
library(gganimate)
library(ggalt)

# Misc
library(tidytext)

# Summary tables
library(gt)
```

## Data

```{r get_data}
tuesdata <- tidytuesdayR::tt_load("2021-01-12")
artwork <- tuesdata$artwork
artists <- tuesdata$artists
```

## Basic exploration

Let's look at the basic dimensions of the data.

```{r}
dim(artwork)
dim(artists)
```

The `artwork` dataset is quite large 

```{r}
artwork %>%
  sample_frac(0.5) %>%
  vis_dat()
```

Let's subset to remove the `NA` columns, unneeded, and rows with missing data.

```{r}
artwork <-
  artwork %>%
  select(-c(
    inscription, thumbnailCopyright, depth,  # Lots of NA values
    thumbnailUrl, url,  # Not needed for now
    accession_number, id, creditLine
    )) %>%
  drop_na()
dim(artwork)
```

Double check our filtering work.

```{r}
artwork %>%
  vis_dat()
```

Save out data for other visualizations when needed.

```{r, eval=FALSE}
# Not run for now
write_csv(artwork, here("data", "artwork.csv"))
```

## Table creation

```{r}
top_20 <-
  artwork %>%
  group_by(artist) %>%
  tally() %>%
  arrange(desc(n)) %>%
  top_n(20)
year_artists <-
  artwork %>%
  select(artist, year) %>%
  group_by(artist) %>%
  mutate(min = min(year),
         max = max(year)) %>%
  select(artist, min, max) %>%
  distinct()
top_20_info <-
  top_20 %>%
  left_join(year_artists) %>%
  select(artist, n, min, max)
top_20_info %>%
  gt() %>%
  tab_header("Top 20 Artists in the Tate Collection") %>%
  cols_label(
    artist = "Artist",
    n = "Count",
    min = "Earliest Year",
    max = "Latest Year"
  )
```

Use dumbell plot to plot above table

https://www.r-bloggers.com/2016/04/ggplot2-exercising-with-ggalt-dumbbells/

```{r}
top_20_info
```

## Questions

https://stackoverflow.com/questions/34522732/changing-fonts-in-ggplot2

### How do the artists' works dominate the Tate collection over time?

Racing bar plot

Inspired: https://stackoverflow.com/a/53163549/6873133

```{r}

```

### Which artists within the Tate collection occupy the largest cumulative area?

Bar plot

```{r}

```

### What is the overall sentiment of the artwork titles?

Chatterplot

https://towardsdatascience.com/rip-wordclouds-long-live-chatterplots-e76a76896098

```{r}

```

### Top artists in the collection, how do their titles differ?

Facetted chatter plot

```{r}

```

### How does the medium of the artwork change over time?

Stacked line plot

```{r}

```

### How often did each artist paint over the years (based on the collection)?

Faceted radar plot https://github.com/ricardo-bion/ggradar

```{r}

```


### How similar are the artists in the collection?

Network analysis, derive distance measure

https://github.com/bnosac/word2vec

- Title
- Medium
- Size
- Year

```{r}

```

