---
title: "Art Collections"
author: "Eric Leung"
date: "2021-01-13"
output: html_document
---

## Setup

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.path = "./figures")

# Utilities
library(tidytuesdayR)
library(readr)
library(here)
library(forcats)

# Data wrangling
library(dplyr)
library(tidyr)
library(tidytext)

# plotting libraries
library(ggplot2)
library(visdat)
library(gganimate)
library(ggalt)

# Misc
library(tidytext)
library(extrafont)
# font_import()  # Import if needed
loadfonts(device = "win")

# Summary tables
library(gt)
```

## Data

```{r get_data}
tuesdata <- tidytuesdayR::tt_load("2021-01-12")
artwork <- tuesdata$artwork
artists <- tuesdata$artists
```

## Basic exploration

Let's look at the basic dimensions of the data.

```{r}
dim(artwork)
dim(artists)
```

The `artwork` dataset is quite large 

```{r}
artwork %>%
  sample_frac(0.5) %>%
  vis_dat()
```

Let's subset to remove the `NA` columns, unneeded, and rows with missing data.

```{r}
artwork <-
  artwork %>%
  select(-c(
    inscription, thumbnailCopyright, depth,  # Lots of NA values
    thumbnailUrl, url,  # Not needed for now
    accession_number, id, creditLine
    ))
dim(artwork)
```

Double check our filtering work.

```{r}
artwork %>%
  vis_dat()
```

Save out data for other visualizations when needed.

```{r, eval=FALSE}
# Not run for now
write_csv(artwork, here("data", "artwork.csv"))
```

## Table creation

```{r}
top_50 <-
  artwork %>%
  group_by(artist) %>%
  tally() %>%
  arrange(desc(n)) %>%
  top_n(50)
year_artists <-
  artwork %>%
  select(artist, year) %>%
  group_by(artist) %>%
  mutate(min = min(year),
         max = max(year)) %>%
  select(artist, min, max) %>%
  distinct()
top_50_info <-
  top_50 %>%
  left_join(year_artists) %>%
  select(artist, n, min, max)
top_50_info %>%
  gt() %>%
  tab_header("Top 50 Artists in the Tate Collection") %>%
  cols_label(
    artist = "Artist",
    n = "Count",
    min = "Earliest Year",
    max = "Latest Year"
  )
```

## Questions

https://stackoverflow.com/questions/34522732/changing-fonts-in-ggplot2

### What is range of years painted of the aquired artwork of top artists?

```{r}
top_50_info %>%
  mutate(artist = fct_inorder(artist)) %>%
  ggplot(aes(x = min, xend = max, y = fct_rev(artist))) +
  geom_dumbbell(size = 1.5,
                dot_guide = TRUE,
                colour = "#a3c4dc",
                colour_xend = "#0e668b",
                dot_guide_size = 0.15) +
  labs(title = "Top 50 Artists in the Tate Collection",
       subtitle = "Artists ranked by number of items in the collection",
       caption = "Data from the Tate Collection https://www.tate.org.uk/") +
  xlab("Year artwork was painted") +
  ylab("Artist") +
  theme_bw() +
  theme(text = element_text(family = "Verdana"),
        plot.background = element_rect(fill = "#f7f7f7"),
        panel.background = element_rect(fill = "#f7f7f7"),
        panel.grid.major.x = element_line(),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank())
```

```{r}
ggsave(here("tidytuesday", "2021", "2021-01-12_art-collections", "top_artists_barbbell.png"),
       width = 5,
       height = 15)
```

```{r}
top_50 %>%
  left_join(artwork) %>%
  mutate(artist = fct_infreq(artist)) %>%
  ggplot(aes(x = year, y = fct_rev(artist))) +
  geom_density_ridges()
```

```{r}
ggsave(here("tidytuesday", "2021", "2021-01-12_art-collections", "top_artists_ridges.png"),
       width = 5,
       height = 15)
```

### How do the artists' works dominate the Tate collection over time?

Inspired by: https://stackoverflow.com/a/53163549/6873133

```{r}
top_50_chasing <-
  top_50 %>%
  # Gather other information about art
  left_join(artwork) %>%
  select(artist, acquisitionYear) %>%
  drop_na() %>%   # Drop artwork with no acquisition year

  # Go by decade because by year would take too long
  mutate(yearDecade = round(acquisitionYear / 10) * 10) %>%
  group_by(artist, yearDecade) %>%
  count(yearDecade) %>%
  arrange(yearDecade) %>%

  # Aggregate collection acquired over time
  group_by(artist) %>%
  mutate(aggcount = cumsum(n)) %>%

  # Fill in missing decades when no art was collected for that artist
  complete(yearDecade = full_seq(yearDecade, 10)) %>%
  mutate(aggcount = spline(x = yearDecade,
                           y = aggcount,
                           xout = yearDecade,
                           method = "hyman")$y) %>%
  mutate(aggcount = ifelse(is.na(aggcount), n, aggcount)) %>%

  # Rank artists by year
  group_by(yearDecade) %>%
  mutate(rank = min_rank(-aggcount) * 1) %>%
  ungroup()
```

```{r}
p <-
  top_50_chasing %>%
  ggplot(aes(x = rank,
             group = artist,
             fill = as.factor(artist),
             color = as.factor(artist))) +
  geom_tile(aes(y = aggcount / 2,
                height = aggcount,
                width = 0.9),
            alpha = 0.8,
            color = NA) +
  geom_text(aes(y = 0,
                label = paste(artist, " ")),
            vjust = 0.2,
            hjust = 1) +
  coord_flip(clip = "off",
             expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE,
         fill = FALSE) +
  labs(title = '{closest_state %>% as.numeric %>% floor}') +
  transition_states(yearDecade,
                    transition_length = 3,
                    state_length = 0.5) +
  enter_grow() +
  exit_shrink() +
  ease_aes('linear')

animate(p,
        fps = 20,
        duration = 15,
        width = 400,
        height = 600,
        end_pause = 10)
```

### Which artists within the Tate collection occupy the largest cumulative area?

Bar plot

```{r}

```

### What is the overall sentiment of the artwork titles?

Chatterplot

https://towardsdatascience.com/rip-wordclouds-long-live-chatterplots-e76a76896098

```{r}

```

### Top artists in the collection, how do their titles differ?

Facetted chatter plot

```{r}

```

### How does the medium of the artwork change over time?

Stacked line plot

```{r}

```

### How often did each artist paint over the years (based on the collection)?

Faceted radar plot https://github.com/ricardo-bion/ggradar

```{r}

```


### How similar are the artists in the collection?

Network analysis, derive distance measure

https://github.com/bnosac/word2vec

- Title
- Medium
- Size
- Year

```{r}

```

