---
title: Global Plastic Waste
author: Eric Leung
---

## Introduction

> This week's dataset is a wine-enthusiast ratings dataset from Kaggle. H/t to
> Georgios Karamanis for sharing this week's dataset as an Issue on our GitHub!
> If you want to submit a dataset, please drop a link and some context as an
> issue. Thanks!
>
> An article with some interesting graphs (different dataset) can be found here.
> They found some clear relationships, but it also appears that cost is factored
> into their rating system. How does the Wine Enthusiast ratings scale compare?

## Load packages

```{r}
library(tidyverse)
```

## Load data

```{r}
wine_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-28/winemag-data-130k-v2.csv")
```

## Exploratory data analysis

**Number of countries**

```{r}
wine_ratings %>%
    distinct(country) %>%
    nrow()
```

**Range of points**

```{r}
wine_ratings %>%
    select(points) %>%
    range()
```

**Range of prices**

```{r}
wine_ratings %>%
    select(price) %>%
    range(na.rm = TRUE)
```

**Amount of missing-ness in data**

```{r}

```

## What is the distribution of words used in describing wine?

```{r}

```

## What is the relationship between price and country?

```{r}

```

## What is the relationship between points and country?

```{r}

```

## What is the relationship between points and price?

```{r}

```
